Mainstreaming Scientific Racism

### 2022-11-04 talk/talk.qmd
tweak talk

Pioneer Fund
: Founded 1937, during the decline of (institutionalized) eugenics

*Mankind Quarterly*
: Founded 1960 by marginalized academics as part of the backlash to *Brown v Board*

@@

The Tobacco Strategy
: Used by regulated industries to create the appearance of legitimate scientific controversy and thereby block or delay regulation [@OreskesMerchantsDoubtHow2011; @FernandezPintoKnowBetterNot2017]

@@

## Corpus {.smallish}

@@

- 3 journals published by American Psychological Association not available
- In B&BS, focal papers + commentaries all bundled together
- PID is missing many relevant book reviews and essays
	- eg, [Rushton's review of Lynn's book on Pioneer](https://www.sciencedirect.com/science/article/pii/S0191886901001337)

<!-- 
\

- Extract article full text from PDF or HTML
- Extract noun phrases using spaCy NLP
 -->

@@

::: {.smaller}
- Custom R package [`tmfast`](https://github.com/dhicks/tmfast)
- 18 different models (3 vocabulary sizes $\times$ $k$ = 5, 10, 20, ..., 50)
:::

@@

# Conclusions {visibility="hidden"}
## Conclusions

- Most Pioneer-funded researchers did not publish heavily in *MQ*
- Race & intelligence research did not appear to originate in *MQ*

@@

- Instead, *Psychological Reports* and later *Intelligence* and *PID* were the primary venues for this psychological form of race science
- "The race science is coming from inside the house!"

>>>>

Pioneer Fund
: Founded 1937, during the decline of (institutionalized) eugenics\
  [@MehlerFoundationFascismNew1989; @TuckerFundingScientificRacism2002]

*Mankind Quarterly*
: Founded 1960 by marginalized academics as part of the backlash to *Brown v Board* [@MehlerFoundationFascismNew1989; @SchafferScientificRacismAgain2007; @JacksonScienceSegregationRace2005 ch. 7]

@@

The Tobacco Strategy
: Used by regulated industries to create the appearance of legitimate scientific controversy and thereby block or delay regulation\
  [@OreskesMerchantsDoubtHow2011; @FernandezPintoKnowBetterNot2017]

@@

## Corpus {}

@@

::: {.aside .smaller}
- 3 journals published by American Psychological Association not available
- In B&BS, focal papers + commentaries all bundled together
- PID is missing many relevant book reviews and essays, eg, [Rushton's review of Lynn's book on Pioneer](https://www.sciencedirect.com/science/article/pii/S0191886901001337)
:::

@@

::: aside
- Custom R package [`tmfast`](https://github.com/dhicks/tmfast)
- 18 different models (3 vocabulary sizes $\times$ $k$ = 5, 10, 20, ..., 50)
:::

@@

# Conclusions {visibility="hidden"}
## Conclusions {.smallish}

- Most Pioneer-funded researchers did not publish heavily in *MQ*
- *MQ* was the primary venue for one of two race science topics
- The other race science topic did not originate in *MQ*

@@

- *MQ* was the primary venue for one form of race science
	- Anthropological? 
- While mainstream journals were the primary venues for a distinct form of race science
	- *Psychological Reports*, later *Intelligence* and *PID*
	- Psychological? 
- "The race science is coming from inside the house!"
